Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
finish substitution proof modulo a few helpers

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \textbf{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\

  \end{array} \]%

@@

    \begin{itemize}
      \item each $PG^A_i$ and $PG_ij$ are related by a bisimulation induced by $f_{pg}$ for thos product graphs
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
      \item each $t_i$ has either $t_i = pfx_{ij}$ or $t_i = \$x$ and $\exists l, (pfx_{ij},l) \in \Gamma(x)$.
    \end{itemize}

    %where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.

  \[ \begin{array}{l}
     \textbf{compile}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ con(\{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
  \end{array} \]%

  \[ \begin{array}{l}
     = con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) )) \\
  \end{array} \]%

>>>>

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \textbf{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
  \end{array} \]%

@@

    \begin{itemize}
      \item each $PG^A_i$ and $PG_ij$ are related by $f_{pg}$
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
    \end{itemize}

  \[ \begin{array}{l}
     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) )) \\
  \end{array} \]%

Unfold definition of compile

  \[ \begin{array}{l}
     ~~~~~ con(\{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
  \end{array} \]%

  Apply the definition of $con$

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow con(rc) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_n) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  Rewrite $con$ on $rc$

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = con(\bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \} \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ con(\{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \} \\
  \end{array} \]%

  \vspace{1em}
  \textbf{Case 1}: Assume $t_i = pfx$. Look at:

  \[ \begin{array}{l}
     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true}) \}) \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
  \end{array} \]%

  Rewrite on $in$ and $out$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b \in f^{-1}(B), (B,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (C,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  \ryan {Proof that we can change this to concrete topology}

  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Since product graphs have equivalent states

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

  \vspace{1em}
  \textbf{Case 2}: Assume $t_i = \$x$

  \[ \begin{array}{l}
     ~~~~~~~~~ con(\{ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
  \end{array} \]%

  Apply the definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Apply definition $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

  Rewrite $con$ on $ma_h$.

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), l_{ij} = \ell) \} \\
  \end{array} \]%

  Apply definition of $con$

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
  \end{array} \]%

  \textbf{Observation}: 
  By filtering the cases where $in = \{ G.s \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$:

 \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

  This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$. This means that the only state in $PG_{ij}$ connected to the start node $G.s$ is a node for $l_{ij}$. This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.

  \vspace{1em}
  \textbf{Merging Cases}:

  In the first case, we got a result of the form:

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

  In the second case, we got a result of the form:

 \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

  Putting these together, we get the following:

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_{ij}~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

  Finally, we observe that this is equivalent to the following:
